%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Awesome Cover Letter
% XeLaTeX Template
% Version 1.3 (30/3/2020)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original authors:
% Claud D. Park (posquit0.bj@gmail.com)
% Lars Richter (mail@ayeks.de)
% With modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template must be compiled with XeLaTeX, the below lines will ensure this
%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt, a4paper]{awesome-cv} % A4 paper size by default, use 'letterpaper' for US letter

\geometry{left=2cm, top=1.5cm, right=2cm, bottom=2cm, footskip=.5cm} % Configure page margins with geometry
 
\fontdir[fonts/] % Specify the location of the included fonts

% Color for highlights
\colorlet{awesome}{awesome-red} % Default colors include: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange, awesome-nephritis, awesome-concrete, awesome-darknight
%\definecolor{awesome}{HTML}{CA63A8} % Uncomment if you would like to specify your own color

% Colors for text - uncomment and modify
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad} % If you would like to change the social information separator from a pipe (|) to something else

%----------------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%----------------------------------------------------------------------------------------

\name{S.A.}{Newaz Saif}
\address{36 Bunnorong Street Tarneit Victoria-3029 Melbourne Australia}
\mobile{(+61) 448-661-986}

\email{snewaz@student.unimelb.edu.au}
%\homepage{www.posquit0.com}
\github{snewaz643}
\linkedin{snewaz643}
%\skype{skypeid}
%\stackoverflow{SOid}{SOname}
%\twitter{@twit}

\position{Software Engineer{\enskip\cdotp\enskip}Data Scientist{\enskip\cdotp\enskip}Tech Entrepreneur} % Your expertise/fields

\quote{``Make the change that you want to see in the world."} % A quote or statement

%----------------------------------------------------------------------------------------
%	RECIPIENT/POSITION/LETTER INFORMATION
%	All of the below lines must be filled out
%----------------------------------------------------------------------------------------

\recipient{Company Recruitment Team}{SEEK Australia\\Level 6, 541 St. Kilda Road\\Melbourne, VIC 3004} % The company being applied to

\letterdate{\today} % The date on the letter, default is the date of compilation

\lettertitle{Job Application for Software Engineering} % The title of the letter

\letteropening{Dear Mr. Dan,} % How the letter is opened

\letterclosing{Sincerely,} % How the letter is closed

\letterenclosure[Attached]{Curriculum Vitae} % Any enclosures with the letter

\makecvfooter{\today}{S.A.Newaz Saif~~~·~~~Cover Letter}{} % Specify the letter footer with 3 arguments: (<left>, <center>, <right>), leave any of these blank if they are not needed
  
%----------------------------------------------------------------------------------------

\begin{document}

\makecvheader % Print the header

\makelettertitle % Print the title

%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------

\begin{cvletter}

%------------------------------------------------

\lettersection{About Me}

Final year undergraduate \textbf{\textit{Bachelor of Science}} student at the \textbf{\textit{University of Melbourne}} pursuing major in \textbf{\textit{Computing and Software Systems}}. I have worked on various frameworks and programming languages with complete exposure to all the IT methodologies with persistent effort and dedication and have done some personal projects with one of my favourite languages, Python shifting between frontend and backend technologies of a \textit{Full Stack Development} scenario. I have enjoyed and excelled in \textit{Algorithms and Data Structures} class and wish to contribute my algorithmic thinking to the company.

%------------------------------------------------

\lettersection{Why Me?}

I have enclosed my CV to support my application. It shows that I would bring important skills to the position, including:

\begin{description}[font=$\bullet$~\normalfont\scshape\color{red!50!black}]
\item [Experience.] I have had the opportunity to work on some bootcamps, hackathons and mostly on personal projects.
\item [Skills.] I am comfortable on a range of programming languages and methodologies which includes Python, Java, SQL, React to name a few.
\item [Performance.] I have always had a passion for technology and especially coding. In August 2016 my coding team became \textit{7th} among top \textit{24} teams in the Victoria Collegiate Programming Competition \textit{4th} among my University peers).
\end{description}

%------------------------------------------------

\lettersection{Why Seek?}

Seek Australia has been the leading job search in the market for quite a while impacting lives of 6 billion people in Australia and they have been quite successful with their magic search algorithm, part of which I would like to learn and add input for enhancement of the job/training based searches. There has been a whole range of changes to their UI/UX and it seems that a lot of creative leaps have been made to their front and backend technologies which I am keen to learn more about.

%------------------------------------------------

\end{cvletter}

%----------------------------------------------------------------------------------------
I would enjoy having the opportunity to talk with you more about this position, and how I could use my skills to benefit your organisation. 

Thank you for considering my application. I look forward to hearing from you.

\makeletterclosing % Print the signature and enclosures

\end{document}